Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-05 paper/paper.tex
added GEO accession

\subsection{Computational analysis of single-cell transcriptomic and viral sequence data}
A computational pipeline that performs all steps in the data analysis is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell}~\citep{russell2018github}. 
This pipeline is orchestrated by \texttt{Snakemake}~\citep{koster2012snakemake}, and begins with the raw sequencing data and ends by generating the figures shown in this paper.
The sequencing data and annotated cell-gene matrix are available on the GEO repository under \jdbcomment{data have been uploaded to GEO, but accession not yet available. The accession number will be added to the README of the GitHub repo at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell} as soon as it's available}.

>>>>

\subsection{Computational analysis of single-cell transcriptomic and viral sequence data}
A computational pipeline that performs all steps in the data analysis is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell}~\citep{russell2018github}. 
This pipeline is orchestrated by \texttt{Snakemake}~\citep{koster2012snakemake}, and begins with the raw sequencing data and ends by generating the figures shown in this paper.
The sequencing data and annotated cell-gene matrix are available on the GEO repository under accession GSE120839 (\url{https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE120839}).
